---
title: "Assignment 5"
author: "Noorah"
date: "11/7/2021"
output: html_document
---

```{r}
###First Loading the libraries 
library(lpSolveAPI)
library(Benchmarking)
```

1. The Hope Valley Health Care Association owns and operates six nursing homes in 
adjoining states. An evaluation of their efficiency has been undertaken using two inputs 
and two outputs. The inputs are staffing labor (measured in average hours per day) and 
the cost of supplies (in thousands of dollars per day). The outputs are the number of 
patient-days reimbursed by third-party sources and the number of patient-days 
reimbursed privately. A summary of performance data is shown in the table below. 


We are going to solve the problem performing DEA analysis. DEA is a  mathematical approach of estimating the best performance standards and then evaluating the relatively efficiency of the entities. These entities (the six nursing homes) are called Decision Making Units (DMUs). We first evaluate each DMU to determine its efficiency along the dimensions that are most favorable to the single DMU, and then for those DMUs that are not fully efficient, we establish a reference set, or technology set, to provide a way for them to improve efficiency. Entities in the technology set are called Peer Units.

One critical assumption in the analysis is that which DMU can belong to this technology set. Our choice of which model to use has significant implications on the technology set and on determining who is efficient and who is not.

We are going to use a specific package for DEA, "Benchmarking", that tells us not only the weights for each DMU, but also the peer units in the hypothetical comparison set (HCUs) and the relative weights needed to make the DMU efficient.

The first step is to create the inputs and outputs by typing both the values and the relative column names. We have two columns of input (matrix x) and two columns of output (matrix y).




```{r}
x <- matrix(c(150, 400, 320, 520, 350, 320,
              0.2, 0.7, 1.2, 2, 1.2, 0.7),
            ncol = 2)
y <- matrix(c(14000, 14000, 42000, 28000, 19000, 14000,
              3500, 21000, 10500, 42000, 25000, 15000),
            ncol = 2)
colnames(x) <- c("Staff Hours", "Supplies")
colnames(y) <- c("Reimbursed Patient Days","Privately Paid Patient Days")
x
y
```



DEA analysis under all DEA assumptions of FDH, CRS, VRS, IRS, DRS, and FRH. 

```{r}
a1 <- dea(x,y,RTS = "fdh")            
a1
peers(a1)  ##Peer identifying                   
lambda(a1) ##Peer weights                    
```

```{r}
a2 <- dea(x,y,RTS = "crs")
a2
peers(a2) ##Peer identifying  
lambda(a2) ##Peer weights
```

```{r}
a3 <- dea(x,y,RTS = "vrs")
a3
peers(a3) ##Peer identifying 
lambda(a3) ##Peer weights
```

```{r}
a4 <- dea(x,y,RTS = "irs")
a4
peers(a4) ##Peer identifying 
lambda(a4) ##Peer weights
```

```{r}
a5 <- dea(x,y,RTS = "drs")
a5
peers(a5) ##Peer identifying 
lambda(a5) ##Peer weights
```

```{r}
a6 <- dea(x,y,RTS = "add")
a6
peers(a6) ##Peer identifying 
lambda(a6) ##Peer weights
```

For conclusion, we will have better estimation whenever we have larger set. 

CRS and DRS give same results,and  both VRS and IRS gave same results.




2. The Research and Development Division of the Emax Corporation has developed three 
new products. A decision now needs to be made on which mix of these products should 
be produced. Management wants primary consideration given to three factors: total 
profit, stability in the workforce, and achieving an increase in the company’s earnings 



The variables that will give the optimal production mix are the quantities of the new products, x1, x2, and x3.

create two variables: 

y1 = 6x1 + 4x2 + 5x3 - 50
y2 = 8x1 + 7x2 + 5x3 - 75

Objective function:

Z = 20x1 + 15x2 + 25x3 - 6y1p - 6y1m -3 y2m

Creating.lp file that contains the formula for this problem using the lpSolveAPI 
```{r}
x <- read.lp("max.lp")
x
```

```{r}
solve(x)
get.objective(x)
get.variables(x)
```

The maximum result Z = 225


x1 = 0
x2 = 0
x3 = 15
y1p = 25
y1m = 0
y2m = 0


Total profit from the production:
P = 25*15 = 375


