---
title: 'Assignment 6'
author: "Noorah"
date: "11/21/2021"
output: html_document
---
1. Consider the following activity-on-arc project network, where the 12 arcs (arrows) represent the 12 activities (tasks) that must be performed to complete the project and the network displays the order in which the activities need to be performed. The number next to each arc (arrow) is the time required for the corresponding activity. Consider the problem of finding the longest path (the largest total time) through this network from start (node 1) to finish (node 9), since the longest path is the critical path.
Formulate
```{r}
###Loading the packages and creating the object
library(lpSolveAPI)
a6 <- make.lp(nrow = 9, ncol = 12) 
```


```{r}
##Naming the arcs and nodes
A.names <- c("X12", "X13", "X24", "X25", "X35", "X46", "X47", "X57", "X58", "X69", "X79", "X89")
N.names <- c("N1", "N2", "N3", "N4", "N5", "N6", "N7", "N8", "N9")
```


```{r}
rownames(a6) <- N.names
colnames(a6) <- A.names
```


```{r}
##Setting the objective function and using -1 to get the min value
of <- c(5, 3, 4, 2, 3, 1, 4, 6, 2, 5, 4, 7)
set.objfn(a6, -1*of)
```


```{r}
##Setting the constraints 
set.row(a6, 1, c(1, 1), indices = c(1, 2))
set.row(a6, 2, c(1, -1, -1), indices = c(1, 3, 4)) 
set.row(a6, 3, c(1, -1), indices = c(2, 5)) 
set.row(a6, 4, c(1, -1, -1), indices = c(3, 6, 7)) 
set.row(a6, 5, c(1, 1, -1, -1), indices = c(4, 5, 8, 9)) 
set.row(a6, 6, c(1, -1), indices = c(6, 10)) 
set.row(a6, 7, c(1, 1, -1), indices = c(7, 8, 11)) 
set.row(a6, 8, c(1, -1), indices = c(9, 12)) 
set.row(a6, 9, c(1, 1, 1), indices = c(10, 11, 12)) 
set.constr.type(a6, rep("="), 9)
rhs <- c(1, rep(0, 7), 1)
set.rhs(a6, rhs)
set.type(a6, 1:12, "binary")


```


```{r}
solve(a6)
get.objective(a6)
get.variables(a6)
```

As what we can see, the longest path is 17 (largest total time) which is from Node1>-Node2>-Node5>-Node7>-Node9







2. Selecting an Investment Portfolio An investment manager wants to determine an opti- mal portfolio for a wealthy client. The fund has $2.5 million to invest, and its objective is to maximize total dollar return from both growth and dividends over the course of the coming year. The client has researched eight high-tech companies and wants the portfolio to consist of shares in these firms only. Three of the firms (S1 – S3) are primarily software companies, three (H1–H3) are primarily hardware companies, and two (C1–C2) are internet consulting companies. The client has stipulated that no more than 40 percent of the investment be allocated to any one of these three sectors. To assure diversification, at least $100,000 must be invested in each of the eight stocks. Moreover, the number of shares invested in any stock must be a multiple of 1000.
The table below gives estimates from the investment company’s database relating to these stocks. These estimates include the price per share, the projected annual growth rate in the share price, and the anticipated annual dividend payment per share.

First lets prepare the decision variables, objective function and constraints:

Decision Variables:

Xi= the number of 1000's shares for each company
X1=S1, X2=S2, X3=S3
X4=H1, X5=H2, X6=H3
X7=C1, X8=C2

Objective Function:
To maximize total dollar return from both growth and dividends over the course of the coming year.
Max Z= Σ Xi* [(price per share * growth rate) + dividend] 
Max Z= 4Xi + 6.5X2 + 5.9X3 + 5.4X4 + 5.15X5 + 10X6 + 8.4X7 + 6.25X8
 
Constraints:


Total Investment: 
40Xi + 50X2 + 80X3 + 60X4 + 45X5 + 60X6 + 30X7 + 25X8 <= 2,500

Diversification:
40Xi + 50X2 + 80X3<=1,000
60X4 + 45X5 + 60X6<=1,000
30X7 + 25X8<=1,000


Min Investment:
40Xi>=100
50X2>=100
80X3>=100
60X4>=100
45X5>=100
60X6>=100
30X7>=100
25X8>=100



1) Determine the maximum return on the portfolio. What is the optimal number of shares to buy for each of the stocks? What is the corresponding dollar amount invested in each stock?



```{r}
library(lpSolveAPI)
##We have 4 constraints and 8 decision variables
lprec <- make.lp(12,8)
```


```{r}
##Set the coefficient of the objective function
set.objfn(lprec, c(4,6.5,5.9,5.4,5.15,10,8.4,6.25))
lp.control(lprec, sense = "max")
```


```{r}
## i will use set.row to set the a column object 

##Total Investment: 
set.row(lprec, 1, c(40,50,80,60,45,60,30,25))

##Diversification
set.row(lprec, 2, c(40,50,80), indices = c(1,2,3))
set.row(lprec, 3, c(60,45,60), indices = c(4,5,6))
set.row(lprec, 4, c(30,25), indices = c(7,8))
##Min Investment:
set.row(lprec, 5, 40, indices = 1)
set.row(lprec, 6, 50, indices = 2)
set.row(lprec, 7, 80, indices = 3)
set.row(lprec, 8, 60, indices = 4)
set.row(lprec, 9, 45, indices = 5)
set.row(lprec, 10, 60, indices = 6)
set.row(lprec, 11, 30, indices = 7)
set.row(lprec, 12, 25, indices = 8)
```


```{r}
##Set corresponding value for max investment and diversification
rhs <- c(2500,1000,1000,1000,100,100,100,100,100,100,100,100)### these numbers are multiply by 1000
set.rhs(lprec, rhs)
```


```{r}
set.constr.type(lprec, c("<=","<=","<=","<=",">=",">=",">=",">=",">=",">=",">=",">="))
```


```{r}
##Setting the boundary 
set.bounds(lprec, lower = rep(1, 8))
```


```{r}
print(lprec)
```


```{r}
##Integer constrains
set.type(lprec, 1:8, "integer")
```

```{r}
solve(lprec)
get.objective(lprec)
get.variables(lprec)
```
Based on the objective function the max reuturn on protfolio with integer restriction is $477,400
The optimum number of shares to buy for each of the stock:
S1=X1=3000 shares = $120,000
S2=X2=5000 shares = $250,000
S3=X3=2000 shares = $160,000
H1=X4=2000 shares = $120,000
H2=X5=3000 shares = $135,000
H3=X6=12000 shares = $720,000
C1=X7=29000 shares = $870,000
C2=X8=5000 shares = $125,000

2) Compare the solution in which there is no integer restriction on the number of shares invested. By how much (in percentage terms) do the integer restrictions alter the value of the optimal objective function? By how much (in percentage terms) do they alter the optimal investment quantities?
So to detrmine this part, I have  run the coding without the integer restriction and here is what I got:

Based on the objective function the max reuturn on protfolio with integer restriction is $487,152.8
The optimum number of shares to buy for each of the stock:
S1=X1=2,500 shares = $100,000
S2=X2=6,000 shares = $300,000
S3=X3=1,250 shares = $100,000
H1=X4=1,666 shares = $99,960
H2=X5=2,222 shares = $99,990
H3=X6=13,333 shares = $799,980
C1=X7=30,000 shares = $900,000
C2=X8=4,000 shares = $100,000

Based on the obove output the integer restiction altered the value of the optimum function by 0.39%

Based on the obove output the integer restiction altered the optimum investment quantities by:

S1= 16.67%
S2= 20%
S3= 37.5%
H1= 16.7%
H2= 25.93%
H3= 11.11%
C1= 3.45%
C2= 20%
